---
title: "p8133_notes1_jsg2145"
author: "Jared Garfinkel"
date: "9/21/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(haven)
library(readxl)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
errorI = vector(mode = "list", length = 100)
power = vector(mode = "list", length = 100)
res = vector(mode = "list", length = 100)
for(i in 1:100) {
  for(j in 1:i) {
    errorI[[c(i, j)]] = 1 - pbinom(j-1, i, 0.25)
    power[[c(i, j)]] = 1 - pbinom(j-1, i, 0.4)
    res[[c(i, j)]] = bind_cols("i" = i, "j" = j, "errorI" = errorI[[c(i, j)]], "power" = power[[c(i, j)]])
  }
  res[[i]] = map(res[[i]], ~bind_rows(.))
}

res %>% 
  bind_rows() %>%
  filter(errorI < 0.05,
         power > 0.8)
```

```{r, eval = FALSE}
stage2errorI = vector(mode = "list", length = 20)
stage1errorI = vector(mode = "list", length = 20)
res = vector(mode = "list", length = 20)
for(i in 1:20) {
  stage1errorI[[i]] = dbinom(i, 20, .25)
  for(j in 1:51){
    stage2errorI[[c(i,j)]] = 1 - pbinom(j-i-1, 71, 0.25)
    res[[c(i,j)]] = bind_cols("n1_response" = i, "n2_response" = j-i, "stage2errorI" = stage2errorI[[c(i,j)]], "stage1errorI" = stage1errorI[[i]])
  }
  res[[i]] = map(res[[i]], ~bind_rows(.))
}

# head(res)

stage1errorI %>% 
  unlist() %>% 
  data.frame()

stage1errorI = bind_rows(stage1errorI)

bind_rows(stage2res) %>% 
  filter(n1_response > 5,
         n1_response+n2_response>23,
         stage2errorI < 0.05,
         stage2power > 0.8)

dbinom(6, 20, .25)
dbinom(1, 20, .25)
dbinom(5, 20, .25)
```

```{r}
output = vector(mode = "list", length = 20)
for (i in 6:20) {
  for(j in 25:51) {
    output[[c(i, j)]] = bind_cols("i" = i, "j" = j, "stage1" = (1-pbinom(i-1, 20, .25)), "stage2" = (1-pbinom(j-1, 51, .25)))
  }
  output[[i]] = map(output[[i]], ~bind_rows(.))
}

bind_rows(output) %>% 
  mutate(n1 = 20,
         n2 = 51) %>%
  summarize(expsize1 = stage1*n1,
            expsize2= sum(stage2*n2)) %>% 
  distinct() %>% 
  summarize(expsize = sum(expsize1, expsize2),
            expsize = sum(expsize))

## 18.23728


(1-pbinom(5, 20, .25))*71 + (pbinom(5, 20, .25)*20)
#39.52419
```

```{r}
output = NULL
for (i in 6:20) {
  output[[i]] = 1-pbinom(i-1, 20, .25)
}
output %>% 
  tibble() %>% 
  unnest() %>% 
  rename("stage1" = ".") %>% 
  mutate(n = 20,
         stage2 = 1 - pbinom(25, 51, .25),
         n2 = 51) %>% 
  summarize(exp = sum(stage1*n+stage2*n2))
# 15.22



```



Under the null, the chances of fewer than 6 responses is `r pbinom(5, 20, .25)`. The chances of moving to the second stage of the trial is `r 1 - pbinom(5, 20, .25)`.

Since the type I error is the Pr(reject H0 under the null), we say that the type I error of the futility round is .3828. This includes all the responses above 5 responses.

```{r}
errorI_alt = vector(mode = "list", length = 51)
power_alt = vector(mode = "list", length = 51)
res_alt = vector(mode = "list", length = 51)
for(i in 1:51) {
  errorI_alt[[i]] = 1 - pbinom(i-1, 51, 0.25)
  power_alt[[i]] = 1 - pbinom(i-1, 51, 0.4)
  res_alt[[i]] = bind_cols("i" = i, "errorI" = errorI_alt[[i]], "power" = power_alt[[i]])
}

bind_rows(res_alt)

```

Since the futility round can include anywhere from 6 to 20 responses, the stage 2 trial can range from 4 to 51 responses to be promising depending on the outcome of the round 1. 

The probability of rejecting the null in stage 2 (given that Sn $\ge$ 6) = `r 1 - pbinom(j-i)

