---
title: "20200926-notes1_jsg2145"
author: "Jared Garfinkel"
date: "9/26/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

Pr(reject the null hypothesis in round 2 | reject the null in round 1) = Pr(reject the null in round 2) * Pr(reject the null in round 1) * Pr(reject the null in round 2)/Pr(reject the null in round 1)

Pr(reject the null in round 1 | reject the null in round 2) = Pr(reject the null in round 2 | reject the null in round 1)*Pr(reject the null in round 1)/ Pr(reject the null in round 2)

Assume they are independent, so Pr(reject the null in round 2 | reject the null in round 1) = Pr(reject the null in round 2 \cap reject the null in round 1) = Pr(reject the null in round 2)*Pr(reject the null in round 1)

```{r}
res = vector(mode = "list", length = 20)
for(i in 1:20) {
  for(j in 1:51){
    res[[c(i,j)]] = bind_cols("n1_response" = i, "n2_response" = j-i)
  }
  res[[i]] = map(res[[i]], ~bind_rows(.))
}

bind_rows(res) %>% 
  mutate(errorI = dbinom(n2_response, 51, .25) * dbinom(n1_response, 20, .25) * (1 - pbinom(5, 20, .25))/(1 - pbinom(23, 71, .25)),
         power = dbinom(n2_response, 51, .4) * dbinom(n1_response, 20, .4) * (1 - pbinom(5, 20, .4))/(1 - pbinom(23, 71, .4))) %>% 
  filter(n1_response > 5,
         n1_response + n2_response > 23) %>% 
  summarize(sum_error = sum(errorI),
            sum_power = sum(power))

```

```{r}

```


